---
title: "R_credit_card_data_project"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

##The aim of this R project is to build a classifier that can detect credit card fraudulent transactions. We will use a variety of machine learning algorithms that will be able to discern fraudulent from non-fraudulent one. By the end of this machine learning project, you will learn how to implement machine learning algorithms to perform classification.


```{r setup, include=FALSE}
library(flexdashboard)
library(ranger)
library(caret)
library(data.table)
library(janitor)
```


##1. Importing the Datasets

##We are importing the datasets that contain transactions made by credit cards + use"janitor" to clean up columns' names.

```{r}
read.csv("creditcard.csv") %>% 
janitor::clean_names() -> data
```


##2. Data Exploration
#In this section of the fraud detection ML project, we will explore the data that is contained in the creditcard_data dataframe. We will proceed by displaying the creditcard_data using the head() function as well as the tail() function. We will then proceed to explore the other components of this dataframe –


#checking the numbers of rows and columns in the dataset.
```{r}
dim(data)

```

#checking the first 6 rows to have an overview.
```{r}
head(data)
```

#chekcing the last part for the dataset.
```{r}
tail(data)
```
#exploring some impoartant data.
```{r}
table(data$class)
```

#exploring average data info.
```{r}
summary(data$amount)
```

#exploring the cloumns names.
```{r}
names(data)
```

#convertign variables.
```{r}
var(data$amount)
```
#checking the stnadard deviation of a vector column.
```{r}
sd(data$amount)
```

##3. Data Manipulation
#In this section of the R data science project, we will scale our data using the scale() function. We will apply this to the amount component of our creditcard_data amount. Scaling is also known as feature standardization. With the help of scaling, the data is structured according to a specified range. Therefore, there are no extreme values in our dataset that might interfere with the functioning of our model. We will carry this out as follows:


```{r}
data$amount = scale(data$amount)
new_data = data [,-c(1)]
head(new_data)
```










Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

